---
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
    toc_depth: 3
    number_sections: true
title: Varying differences between police forces
---

```{r,echo=F}
source("markdown_functions.R")
source("model_power_vs_police_force_variance.R")
```

# Simulation overview

The baseline rates were varied between police forces to varying extents to see what impact this would have on model power for each of the outcomes.

The simulation was characterised by the amount of variation applied as a percentage to some specified base rate for each outcome.

The following variations were applied: `r policeForceVariabilities`

# Results

The table below shows the fraction of 1000 simulations that had a "significant" model outcome at 0.05 for each of the configurations tested.

```{r,echo=F}
if(F) {
comparisonMelted <- melt(comparisonTable, id.vars = "Outcome", variable.name = "Model", value.name = "Value",variable.factor=F)
comparisonMelted[,BetweenForceVariance:=gsub(".*_PV(.*)_1000","\\1",Model)]
comparisonMelted2 <- dcast(comparisonMelted, Model ~ Outcome, value.var = "Value")
names(comparisonMelted2) <- c("Model","Rehab","Hospital","Reoffend")
# add in the "variability" as SDs
comparisonMelted2[,RehabSD:=lapply(configList[Model],function(cfg) {cfg$effects$rehab$baseline_sd})]
comparisonMelted2[,HospitalSDG1:=lapply(configList[Model],function(cfg) {cfg$effects$hospitalisation$group1$baseline_sd})]
comparisonMelted2[,HospitalSDG2:=lapply(configList[Model],function(cfg) {cfg$effects$hospitalisation$group2$baseline_sd})]
comparisonMelted2[,ReoffendSD:=lapply(configList[Model],function(cfg) {cfg$effects$reoffending$baseline_sd})]

comparisonSeparated <- lapply(c("AllForces","First6","First12"),function(selection) {
   d <- comparisonMelted2[str_detect(comparisonMelted2$Model,selection)]
   d[,BetweenForceVariance:=gsub(".*_PV(.*)_1000","\\1",Model)]
   d[,Model:=NULL]
   setkey(d,"BetweenForceVariance")
   setcolorder(d,c("BetweenForceVariance","Rehab","Hospital","Reoffend"))
   names(d) <- c("BetweenForceVariance",paste(selection,c("Rehab","Hospital","Reoffend"),sep="_"))
   d
})

outputTable <- Reduce(function(a,b) { merge(a,b,on="BetweenForceVariance") },comparisonSeparated)
# order this so we group by force selection all,first12,first6
setcolorder(outputTable,c(1,2,8,5,3,9,6,4,10,7))
#names(outputTable) <- c("BetweenForceVariance",rep(c("All","First12","First6"),3))

kable(outputTable,"html") %>% 
   kable_styling("basic") %>% 
   #column_spec(1, border_right = "solid") %>%
   column_spec(1, extra_css = "border-right: solid 1px lightgrey;") %>%
   column_spec(4, extra_css = "border-right: solid 1px lightgrey;") %>%
   column_spec(7, extra_css = "border-right: solid 1px lightgrey;") %>%
   column_spec(10, extra_css = "border-right: solid 1px lightgrey;") %>%
   add_header_above(header=c(" "=1,"Rehab"=3,"Hospital"=3,"Reoffend"=3))
}
```

## Hospitalisation

### Group 1 (Casual offenders)

```{r,echo=F,fig.width=8,fig.height=8}
plot_hosp_power_vs_pf_sd_g1()
# save it to PNG
savedPlot <- recordPlot()
png(filename = "figures/hospital_vs_pf_nogroup1_g1.png", width = 600, height = 600)
replayPlot(savedPlot)
invisible(dev.off())
```

### Group 2 (Persistent offenders)

```{r,echo=F,fig.width=8,fig.height=8}
plot_hosp_power_vs_pf_sd_g2()
# save it to PNG
savedPlot <- recordPlot()
png(filename = "figures/hospital_vs_pf_nogroup1_g2.png", width = 600, height = 600)
replayPlot(savedPlot)
invisible(dev.off())
```

### PF data

#### All forces

```{r,echo=F}
kable(modelTestData$pf) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "center")
```

#### First 12

```{r,echo=F}
kable(modelTestData$pf[1:12]) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "center")
```

#### First 6

```{r,echo=F}
kable(modelTestData$pf[1:6]) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "center")
```

#### Summaries

```{r,echo=T}
summary(modelTestData$pf)

summary(modelTestData$pf[1:12])

summary(modelTestData$pf[1:6])
```
